\chapter{Information about the master's programmes}

This \ifanappendix appendix \else chapter \fi gives an overview of the master's
programmes of the Faculty of Engineering. These master's programmes are
supported by default by the LaTeX document class \cls{kulemt}. But all of this
information is also valid for non-LaTeX documents.

A first section gives an overview of the predefined master's programme colours.
The second section describes the additional information which is stored in the
\file{kulemt.cfg} configuration file.

\section{Master's programme colours}
\label{sec:mastercolors}
The master's programme colours are shown below for all master's programmes which
have colours defined by the Faculty of Engineering. These are the official
colours, which means that only the Faculty can change them. If a master's
programme wants to have its colours added or changed, it should contact the
Faculty secretary.

All colours should be defined as coordinates in the \acro{CMYK} colour space
which is normally used by printers. White corresponds to $(0,0,0,0)$ and
black to $(0,0,0,1)$ in \acro{CMYK}.

\begingroup
\makeatletter
\let\kulemt@end@master@def\endinput
\renewcommand*\kulemt@def@master[2]{%
  \kulemt@set@master#2{}{}{}\@nil
  \ifx\kulemt@master@colors\@empty\else
    \par\bigskip
    \expandafter\kulemt@getcolors\kulemt@master@colors::\@nil
    \centerline{\fboxsep\z@
      \expandafter\colorbox\kulemt@color@bg{%
        \vbox to 11mm{\vss \centering
          \fontencoding{T1}\fontfamily{kulemtfpf}%
          \fontseries\bfdefault\selectfont
          \expandafter\textcolor\kulemt@color@fg{%
            \kulemt@master@title}\vss}}}\nobreak
    \centerline{%
      Background colour: \expandafter\printcolor\kulemt@color@bg\@nil\hfill
      Text colour: \expandafter\printcolor\kulemt@color@fg\@nil}%
  \fi}
\newcommand*\printcolor{\@ifnextchar[\printcolor@\printcolor@@}
\newcommand*\printcolor@{}
\def\printcolor@[#1]#2\@nil{$(#2)$%
  \uppercase{\def\@tempa{#1}}\def\@tempb{CMYK}%
  \ifx\@tempa\@tempb\else ~in~\acro\@tempa!\fi}
\newcommand*\printcolor@@{}
\def\printcolor@@ #1\@nil{\def\@tempa{#1}%
  \def\@tempb{black}\ifx\@tempa\@tempb $(0,0,0,1)$\else
    \def\@tempb{white}\ifx\@tempa\@tempb $(0,0,0,0)$\else #1\fi\fi}
\input{kulemt.cfg}
\endgroup

\section{Additional information from \file{kulemt.cfg}}\label{sec:mastercfg}
The master's programme specific information is stored in the \file{kulemt.cfg}
file. Apart from the master's programme colour information described in the
previous section, it contains information about the master's programme
language, the programme's faculty, known master's programme options, and
copyright contact information.

\begingroup
\makeatletter
\@ifundefined{microtypesetup}{}{\microtypesetup{protrusion=false}}%
\let\kulemt@end@master@def\endinput
\def\ProvidesFile #1[#2]{%
  This section describes the \file{#1} file dated \printdateTeX{#2}.
  If no faculty name is shown, it is an inter-faculty
  master's programme.\par\raggedright}
\renewcommand*\kulemt@div@master[1]{\subsection{#1}}
\sideparswitchfalse \reversesidepartrue
\newcommand*\optionHangfrom{}
\newcommand*\handleOption[2]{%
  \ifvmode \@hangfrom{\optionHangfrom}\else \break \fi
  \textbf{--} \ \texttt{#1} (`#2')}
\newcommand*\printmasterinfo[2]{\par
  \addvspace\medskipamount \parindent\z@
  \kulemt@filingcardfalse \kulemt@set@master#2{}{}{}\@nil
  \leavevmode\sidepar{\raggedleft\texttt{#1}}\textsc{\kulemt@master@title}\par
  \nobreak \expandafter\MakeUppercase\kulemt@master@language\space master%
  \edef\@tempa{\kulemt@fac@name}\ifx\@tempa\@empty\else\space of the \@tempa\fi.
  % A filing card is \ifkulemt@filingcard\else not \fi required.
  \par
  \nobreak \@hangfrom{Contact info: }\kulemt@contact@print\par
  \nobreak
  \ifx\kulemt@master@options@vl\relax
    The master's programme doesn't allow you to mention an option.%
  \else\ifx\kulemt@master@options@vl\@empty
    The master's programme doesn't require you to mention an option.%
  \else
    One of the following master's programme options \emph{must} be used:
    \def\@tempb{}\@for\@tempa:=\kulemt@master@options@vl\do{%
      \@tempb\texttt{\@tempa}\def\@tempb{, }}.%
  \fi\fi \par
  \@tempswatrue \ifx\kulemt@master@options@v\@empty
    \ifx\kulemt@master@options@o\@empty \@tempswafalse \fi\fi
  \if@tempswa
    \nobreak Known master's programme option abbreviations:\par%\tracingall
    \ifx\kulemt@master@options@v\@empty\else
      \def\optionHangfrom{\quad}%
      \nobreak \kulemt@handle@mo\kulemt@master@options@v\handleOption \par
    \fi
    \ifx\kulemt@master@options@o\@empty\else
      \def\optionHangfrom{\quad obsolete: \ }%
      \nobreak \kulemt@handle@mo\kulemt@master@options@o\handleOption \par
    \fi
  \fi}
\let\kulemt@def@master\printmasterinfo
\newif\ifobsoletemaster
\renewcommand*\kulemt@obsolete@master[3][]{\obsoletemastertrue}
\input{kulemt.cfg}
\subsection{Obsolete master's programmes}\label{sec:obsoletemasters}
\ifobsoletemaster
  \def\ProvidesFile #1[#2]{}
  \let\kulemt@div@master\@gobble
  \renewcommand*\kulemt@def@master[2]{}
  \renewcommand*\kulemt@obsolete@master[3][]{%
    \printmasterinfo{#2\if &#1&\else .#1\fi}{#3}}
  \input{kulemt.cfg}
\else
  In this file, no obsolete master's programmes are defined.\par
\fi
\endgroup

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "kulemt"
%%% End: 
